---
title: "Analysis of Hotel Reviews and Their Impacts"
author: "Hui-Yi Kao, Michelle Wu, Nana Wang"
date: "11/14/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Source Information
```{r}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)
source("../source/data_access.R")
source("../source/chart-1_code.R")
source("../source/chart-2_code.R")
source("../source/chart-3_code.R")
source("../source/table.R")
source("../source/summary_info.R")
```

### Dynamic Paragraph
```{r}
summary_info
```
In this analysis, we are using the data to detect the relationship among various factors in the largest dataset of our project, which includes overall score, cleanliness, value for money, and etc. For example, we found out that the maximum result of the review is a hotel named "Best Western Hollywood Plaza Inn." On the other hand, two of the highest overall reviews are hotels named "Selby Ave Guest House" and "Double Suite in Santa Monica" with the score of 10/10. The correlation between the overall score and cleanliness is significant that we discovered that the cleanest hotels also include these two hotels. We found out that LA Deluxe Suite at The Grove Mall is the most worth price hotel among other hotels while Modern Star Apartments is the closest hotel to the center of the city. (0.6 miles from center) 

## Table
```{r}
new_data
```
This table is a new data set that we filtered down the NA values in number_of reviewers, and we group by the name of the hotels to find the maximum number of reviewers in this new data. Finally, we select the top 15 hotels that have the most reveiws from booking.com


```{r review_from_booking}
summary(review_from_booking)
```

## Three Charts

```{r overall_price_corr, echo=FALSE}
#plot(pressure)
overall_price_corr
bar_graph
pie_chart
```

### Charts Summary
#### Chart 1 Descriptive paragraph
We made a scatterplot to analyze the correlation between the overall score and price on booking.com website. However, we omitted some observations that contain missing values. As a result, in this scatterplot, we can detect a positive correlation between the overall score and the price. This result answers one of the research questions we created on the project proposal.

#### Chart 2 Descriptive paragraph
This is a bar graph that shows the top 15 hotels that got the most reviews from booking.com. However, in our code, there are some issues that there are some hotels who receive a few reviews but are shown in the bar graph. (to be fixed) In this visualization, we want to focus on the hotels that get most reviews and compared them with more detailed variables such as location, cleanliness, facilities, and more in our future report. 

#### Chart 3 Descriptive paragraph
This pie chart displays the percentage each rating holds in the Trip Advisor Hotel Reviews dataset. By aggregating the data and calculating the percentage of 1, 2, 3, 4, and 5-star ratings, we were able to display it in a pie chart that is labeled with each respective percentage. This is helpful in helping us
generalize the data and analyze and compare the largest and smallest groups. 

